### 2019-08-19 maciek.tex
A sketch of the lower-bound

Model assumes the existence of a perfect partition of the input graph.
We present a lower-bound for the competitive ratio of $\Omega(\ell)$ for any deterministic algorithm.
To this end, we use $k = 3$, i.e., the capacity of each server is $3$.

@@

Then, we issue a request $(x, y)$.

>>>>

Model assumes the existence of a perfect partition of the input graph.
We present a lower bound for the competitive ratio of $\Omega(\ell)$ for any deterministic algorithm.
To this end, we use $k = 3$, i.e., the capacity of each server is $3$.

@@

Note that the adversary can foresee the actions of the algorithm, and may choose $D$ in such way, that $x$ cycles through all other clusters before reaching $D$, paying the cost of $\Omega(k)$, which would already suffice to show the lower bound.

Then, $x$ and $y$ have the same color, and we issue a request $(x, y)$. As these have the same color (and there are different than $d_1, d_2$ and $d_3$), OPT pays no cost for this request, and ALG pays $2$ for migrating $x$ and $y$ to other cluster.
We repeat the entire process, i.e., we force ALG to choose $x$ and $y$ of the same color, and issue such request that is free for OPT. This process can continue until ALG has no more clusters with singleton components, or it pays the cost $\Omega(k)$ already.
